|

### 2023-07-16 paper/04-results.Rmd
edited icc table and text

Next, Table \ref{tab:icc} displays the intraclass correlation coefficients (ICC) for the three different grouped terms, describing the proportion variance explained between the group terms in comparison to the residual variance.
While the residual variance is unsurprisingly the largest value, between the three group terms, we observe the largest ICC for pass rushers, followed by the QB, and the blocker.
This emphasizes how STRAIN is mostly attributable to pass rushers, but is necessary to adjust for opposition and other factors.

@@

\begin{table}[ht]
\caption{Intraclass correlation coefficients for the multilevel model for average STRAIN. \label{tab:icc}}
\centering
\begin{tabular}{lr}
\hline
Group & ICC \\ 
\hline
Pass rusher & 0.0365 \\ 
Pass blocker & 0.0098 \\ 
Defensive team & 0.0134 \\ 
Offensive team & 0.0143 \\
Residual & 0.9260 \\ 
\hline
\end{tabular}
\end{table}

>>>>

Next, Table \ref{tab:icc} displays the intraclass correlation coefficients (ICC) for the four different groupings, describing the proportion variance explained between the group terms in comparison to the residual variance.
While the residual variance is unsurprisingly the largest value, between the player and team factors, we observe the largest ICC for pass rushers, followed by the offensive and defensive teams, and the blocker.
This emphasizes how STRAIN is mostly attributable to pass rushers, but is necessary to adjust for opposition and other factors.

@@

<!-- \begin{table}[ht] -->
<!-- \caption{Intraclass correlation coefficients for the multilevel model for average STRAIN. \label{tab:icc}} -->
<!-- \centering -->
<!-- \begin{tabular}{lr} -->
<!-- \hline -->
<!-- Group & ICC \\  -->
<!-- \hline -->
<!-- Pass rusher & 0.0365 \\  -->
<!-- Pass blocker & 0.0098 \\  -->
<!-- Defensive team & 0.0134 \\  -->
<!-- Offensive team & 0.0143 \\ -->
<!-- Residual & 0.9260 \\  -->
<!-- \hline -->
<!-- \end{tabular} -->
<!-- \end{table} -->

\begin{table}[ht]
\caption{Intraclass correlation coefficients for the multilevel model for average STRAIN. \label{tab:icc}}
\centering
\begin{tabular}{cccccc}
\hline
\text{ } & Pass rusher & Pass blocker & Defensive team & Offensive team & Residual \\ 
\hline
ICC & 0.0365 & 0.0098 & 0.0134 & 0.0143 & 0.9260 \\ 
\hline
\end{tabular}
\end{table}
